### 2021-08-23 plos_latex_template.tex
RJ: added money rule

>>>>

\section{Rule X: Do not expect the organizing team to work full time and for free}

Having a diverse team and executing inclusive and accessible practices throughout the organizing period --it might be a year or two --may require a lot of effort. The effort is worth it because it strengthens the event and the community making it truly welcoming for everyone. However, having a strong community as the only reward may be enough if you are in a privileged position. Some people and often the minoritized ones do not have institutional support to put time and effort into the organization tasks and do not have the luxury to commit to the organization for free. In addition, tasks such as taking and responding to code of conduct reports, can be emotionally intense work and should be additionally rewarded. Be mindful of each particular context, be flexible with hours or commitments, and revise your budget; if possible, secure funds to offer stipends to them early on.
